---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: ../article/chicago-ff.bst
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

[^freire]: School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <http://danilofreire.github.io>.

[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, <davidskarbek@brown.edu>, <http://davidskarbek.com>.

\appendix

# Descriptive Statistics

```{r loading, warning=F, message=F, error=F, cache=T, echo=F}
# Install and load required packages
packages <- c("bartCause", "cjoint", "cregg", "estimatr", "kableExtra",
              "janitor", "quanteda", "seededlda", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

# Load the dataset, remove unused rows and columns,
# and convert variable names to snake case
df <- read_csv("../data/data.csv") %>%
  clean_names() %>%
  mutate(response_id            = as.character(response_id),
         consent                = as.factor(q1),
         progress               = as.numeric(progress),
         finished               = as.factor(finished),
         age                    = as.numeric(q2),
         gender                 = as.factor(q3),
         race                   = as.factor(q4),
         education              = as.factor(q5),
         region                 = as.factor(q6),
         household_income       = as.factor(q7),
         ideology               = as.factor(q8),
         death_penalty          = as.factor(q9),
         previous_victim        = as.character(q10),
         previous_victim_text   = as.character(q10_text),
         views_police           = as.factor(q11),
         views_justice          = as.factor(q12),
         exp01_control          = as.numeric(q18),
         exp01_police           = as.numeric(q19),
         exp01_slow_justice     = as.numeric(q20),
         exp01_small_punishment = as.numeric(q21),
         exp03_control          = as.numeric(q22),
         exp03_constitution     = as.numeric(q23),
         exp03_rights           = as.numeric(q24),
         exp03_vendetta         = as.numeric(q25)) %>%
  slice(-1L) %>%
  select(-c(q1:q12, q18:q25)) %>%
  relocate(response_id, consent, progress, finished,
           location_latitude, location_longitude) %>%
  mutate(across(where(is.character), tolower)) %>%
  mutate(across(where(is.factor), tolower))

# Translate factor values from Portuguese to English
df <- df %>%
  mutate(consent = recode(consent,
                          concordo       = "Agree",
                          `não concordo` = "Disagree"),
         gender = recode(gender,
                         "feminino"              = "Female",
                         "masculino"             = "Male",
                         "outro"                 = "Other",
                         "prefiro não responder" = "Rather Not Say"),
         race = recode(race,
                       "amarela"               = "Asian",
                       "branca"                = "White",
                       "indígena"              = "Indigenous",
                       "outra"                 = "Other",
                       "parda"                 = "Mixed Race",
                       "prefiro não responder" = "Rather Not Say",
                       "preta"                 = "Black"),
         race = fct_relevel(race, "Other", "Rather Not Say", after = Inf),
         education = recode(education,
                            "da 1ª à 4ª série do ensino fundamental (antigo primário)" = "Primary School",
                            "da 5ª à 8ª série do ensino fundamental (antigo ginásio)"  = "Secondary School",
                            "ensino médio (antigo 2º grau)"                            = "High School",
                            "ensino superior"                                          = "College",
                            "mestrado ou doutorado"                                    = "Graduate School",
                            "não sei"                                                  = "Don't Know"),
         education = fct_relevel(education, "Primary School", "Secondary School", "High School",
                                 "College", "Graduate School", "Don't Know"),
         region = recode(region,
                         "centro-oeste" = "Center-West",
                         "nordeste"     = "Northeast",
                         "norte"        = "North",
                         "sudeste"      = "Southeast",
                         "sul"          = "South"),
         household_income = recode(household_income,
                                   "acima de r$ 20.000"       = "Above R$20,000",
                                   "até r$ 1.000"             = "Up to R$1,000",
                                   "de r$ 1.001 a r$ 2.000"   = "From R$1,001 to R$2,000",
                                   "de r$ 10.000 a r$ 20.000" = "From R$10,001 to R$20,000",
                                   "de r$ 2.001 a r$ 3.000"   = "From R$2,001 to R$3,000",
                                   "de r$ 3.001 a r$ 5.000"   = "From R$3,001 to R$5,000",
                                   "de r$ 5.001 a r$ 10.000"  = "From R$5,001 to R$10,000"),
         household_income = fct_relevel(household_income, "Up to R$1,000",
                                        "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
                                        "From R$3,001 to R$5,000", "From R$5,001 to R$10,000",
                                        "From R$10,001 to R$20,000", "Above R$20,000"),
         ideology = recode(ideology,
                           "centro"                = "Center",
                           "centro-direita"        = "Center-Right",
                           "centro-esquerda"       = "Center-Left",
                           "direita"               = "Right",
                           "esquerda"              = "Left",
                           "não sei"               = "Don't Know",
                           "prefiro não responder" = "Rather Not Say"),
         ideology = fct_relevel(ideology, "Left", "Center-Left", "Center",
                                "Center-Right", "Right", "Don't Know",
                                "Rather Not Say"),
         death_penalty = recode(death_penalty,
                                "não"                   = "No",
                                "não sei"               = "Don't Know",
                                "prefiro não responder" = "Rather Not Say",
                                "sim"                   = "Yes"),
         death_penalty = fct_relevel(death_penalty, "Don't Know",
                                     "Rather Not Say", after = Inf),
         views_police = recode(views_police,
                               "boa"                   = "Good",
                               "muito boa"             = "Very Good",
                               "muito ruim"            = "Very Bad",
                               "não sei"               = "Don't Know",
                               "prefiro não responder" = "Rather Not Say",
                               "regular"               = "Regular",
                               "ruim"                  = "Bad"),
         views_police = fct_relevel(views_police, "Very Good", "Good", "Regular",
                                    "Bad", "Very Bad", "Don't Know", "Rather Not Say"),
         views_justice = recode(views_justice,
                                "boa"                   = "Good",
                                "muito boa"             = "Very Good",
                                "muito ruim"            = "Very Bad",
                                "não sei"               = "Don't Know",
                                "prefiro não responder" = "Rather Not Say",
                                "regular"               = "Regular",
                                "ruim"                  = "Bad"),
         views_justice = fct_relevel(views_justice, "Very Good", "Good", "Regular",
                                    "Bad", "Very Bad", "Don't Know", "Rather Not Say"),
         previous_victim_dummy = recode(previous_victim,
                                        "nenhum" = "No",
                                        .missing = NA_character_,
                                        .default = "Yes")) %>%
  relocate(response_id:previous_victim, previous_victim_dummy,
           previous_victim_text:f_5_2_8)

df1 <- df %>% filter(consent == "Agree")
```

This appendix contains additional tables and graphs that complement the results
we present in "_Vigilantism and Institutions: Understanding Attitudes towards
Lynching in Brazil_". An extended version of this file, which includes further
tests for heterogeneous effects and `R` code, is available at [_redacted for
peer review_]. The repository also contains our pre-analysis plan and the `php`
scripts we used in our conjoint experiment.

We ran our survey experiments from October 30 to December 14, 2020 via
Qualtrics. Our sample includes `r nrow(df1)` Brazilians older than 18 years of
age from the five regions of the country (Center-West, North, Northeast, South,
and Southeast). 

## Gender

The gender distribution of our sample closely matches
the official data from the [Brazilian Census
Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18320-quantidade-de-homens-e-mulheres.html),
which states that women are 51.8% of the population and men comprise 48.2%.

\footnotesize
```{r gender, warning=F, error=F, cache=T, echo=F}
df1 %>%
  group_by(gender) %>%
  filter(!is.na(gender)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Gender = gender) %>%
  kbl(., booktabs = TRUE, caption = "Gender") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

## Age

The age distribution of our sample is shown below. The median age of the survey
respondents is `r round(median(df1$age, na.rm=T), 1)` years old, which
indicates that our sample is older than the Brazilian population (median age $=
33.4$ years old) [@ciafactbook2020].

\footnotesize
```{r age, warning=F, error=F, cache=T, fig.width=6, fig.height=4.3, echo=F}
tibble(` `    = "Age",
       Median = round(median(df1$age, na.rm = TRUE), 2),
       Mean   = round(mean(df1$age, na.rm = TRUE), 2),
       SD     = round(sd(df1$age, na.rm = TRUE), 2),
       Min    = min(df1$age, na.rm = TRUE),
       Max    = max(df1$age, na.rm = TRUE),
       `NA`   = sum(is.na(df1$age))) %>%
kbl(., booktabs = TRUE, caption = "Age") %>%
row_spec(0, bold = TRUE) %>%
kable_styling(latex_options = "hold_position")

ggplot(subset(df1, !is.na(age)), aes(age)) +
  geom_bar(fill = "#152238") +
  labs(title = "Age Distribution", x = "Age", y = "Count") +
  geom_vline(aes(xintercept = mean(age, na.rm = TRUE)),
            color = "darkred", linetype = 5, size = 0.5) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
```
\normalsize

## Race

The next demographic variable we show here is race. According to the [Brazilian
Census Bureau](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18319-cor-ou-raca.html),
42.7% of the Brazilian population identify as White, 46.8% as Mixed Race, 9.4%
as Blacks, and 1,1% as Asians or Indigenous. As we see below, our sample
includes more Whites and fewer individuals who identify as Mixed Race. The
number of Blacks roughly coincide with the population statistics.

\footnotesize
```{r race, warning=F, error=F, cache=T, echo=F}
df1 %>%
  rename(Race = race) %>%
  mutate(Race = fct_relevel(Race, "White", "Other", "Rather Not Say", after = Inf)) %>%
  group_by(Race) %>%
  filter(!is.na(Race)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Race") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

## Education

```{r educationtext, echo=F, warning=F, error=F, cache=T, echo=F}
df2 <- df1 %>%
  group_by(education) %>%
  filter(!is.na(education)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Education = education)
```

As expected, our sample is also more educated than [the Brazilian
population](https://educa.ibge.gov.br/jovens/conheca-o-brasil/populacao/18317-educacao.html).
About `r df2[4, 3]*100`% of the respondents have a college degree, and `r df2[3, 3]*100`%
have graduate school education.

\footnotesize
```{r education, warning=F, error=F, cache=T, echo=F}
df1 %>%
  rename(Education = education) %>%
  mutate(Education = fct_relevel(Education, "Primary School", "Secondary School",
                                 "High School", "College", "Graduate School")) %>%
  group_by(Education) %>%
  filter(!is.na(Education)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Education") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

## Household Income

```{r income-text, echo=F, warning=F, error=F, cache=T, echo=F}
df2 <- df1 %>%
  group_by(household_income) %>%
  filter(!is.na(household_income)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Household Income` = household_income)
```

In terms of household income, `r df2[5, 3]*100`% of the respondents earn from
R\$5,0001 to R\$10,000 per month (US\$915 to US\$1830 as of January 2021), which
comprise the largest group in our sample. However, the sample also contains
`r df2[2, 3]*100`% of participants whose household income ranges between R\$1,001
and R\$2,000 (US\$ 184 to US\$368) and `r df2[1, 3]*100`% with household incomes
up to R\$1,000, which is roughly equivalent to Brazil's monthly minimum wage. In
this respect, we have reached participants from all social classes.

\footnotesize
```{r income, warning=F, error=F, cache=T, echo=F}
df1 %>%
  rename(`Household Income` = household_income) %>%
  mutate(`Household Income` = fct_relevel(`Household Income`, "Up to R$1,000",
                                          "From R$1,001 to R$2,000", "From R$2,001 to R$3,000",
                                          "From R$3,001 to R$5,000", "From R$5,001 to R$10,000",
                                          "From R$10,001 to R$20,000", "Above R$20,000")) %>%
  group_by(`Household Income`) %>%
  filter(!is.na(`Household Income`)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Household Income") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

## Political Ideology

```{r ideologytext, echo=F, warning=F, error=F, cache=T, echo=F}
df2 <- df1 %>%
  group_by(ideology) %>%
  filter(!is.na(ideology)) %>%
  mutate(ideology = fct_relevel(ideology, "Left")) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(Ideology = ideology)
```

We have also collected information regarding the subjects' political ideology.
Most respondents identify themselves as right-wingers (`r df2[5, 3]*100`%),
followed by left-wingers (`r df2[1, 3]*100`%), and centrists (`r df2[3, 3]*100`%).
Subjects who do not know their ideology or prefer not to tell their
political beliefs are also large in number (`r df2[6, 3]*100`% and
`r df2[7, 3]*100`%, respectively).

\footnotesize
```{r ideology, warning=F, error=F, cache=T, echo=F}
df1 %>%
  rename(Ideology = ideology) %>%
  mutate(Ideology = fct_relevel(Ideology, "Left", "Center-Left", "Center",
                                "Center-Right", "Right")) %>%
  group_by(Ideology) %>%
  filter(!is.na(Ideology)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  kbl(., booktabs = TRUE,  linesep = "", caption = "Political Ideology") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

# Experiment 01

## Description

In our first experiment, we analyze how respondents justify their preferences
towards extralegal violence. We assess the impact of three factors that have
been cited as major drivers of lynchings: 1) police ineffectiveness; 2) slow
criminal justice; 3) demand for harsher punishment for criminals. Below, we
discuss them in further detail.

Research shows that police ineffectiveness frequently appears as a strong
predictor of vigilantism [@garcia2019anger]. The direct result of the weakness
of police institutions is that citizens decide to take criminal matters "into
their own hands", thus persecuting and punishing the criminals by themselves. A
recent statistic indicates that the police solves only 10% of the homicides in
Brazil, which lends support to the link between weak law enforcement and
lynchings [@pearson2018latam].

Another possible determinant of lynching support is lack of trust in the
justice system [@smith2019contradictions]. This is often due to long criminal
proceedings, which cause significant anxiety for the victims. In Brazil, the
penal code allows the accused to appeal each decision several times, so it can
take decades before a criminal case is closed [@sousa2005utilizaccao]. In this
respect, citizens do not believe that, even if the criminal is put to trial,
he/she will be punished in a timely matter. Note that although the police is
technically part of the criminal justice system, we analyze the two
institutions separately in our experiment.

Lastly, we evaluate whether respondents think that the legal punishment
assigned to criminals is not proportional to the severity of their crimes. In
particular, we intend to gauge the demand for iron-fisted criminal justice in
Brazil. Although this treatment arm is related to the previous ones, it
addresses not the efficiency of the institutions, but their legitimacy
[@nivette2016institutional]. In fact, Brazilians are often vocal about their
preference for repressive legal punishment. In a recent article in _The Wall
Street Journal_, a bar owner justified the lynching of the local thug who
killed his son by saying that "_even if he had been put behind bars for 100
years it wouldn't have been enough to pay for all his crimes_"
[@pearson2018latam]. We hypothesize that many Brazilians also share this view.

The experiment consists of three treatment conditions and one control group.
Respondents read an excerpt of a news article describing a real lynching case.
We have slightly edited the original text so that respondents have no prior
knowledge of the crime.[^jornal] The vignette for the control group includes no
information about the reasons behind the lynching. We ask respondents to show
their level of lynching support using a 0-100 slider, where 0 means no support
and 100 means full support. Respondents in each of the three treatment arms
read the same piece, but with one additional sentence explaining the
motivations behind the lynching. The vignettes are as follows:

[^jornal]: The original article is available at the following address:
<https://jr.jor.br/2020/05/01/homem-e-linchado-na-vila-progresso>.
Access: August 2020.

* *Control group*: A man was lynched last Friday in Jundiaí, São Paulo.
  According to the neighbours, he tried to break into a house but was
  immobilised and beaten by members of the community.[^control-exp01]

[^control-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade.

* *Treatment 01 - Police ineffectiveness*: A man was lynched last Friday in
  Jundiaí, São Paulo. According to the neighbours, he tried to break into a
  house but was immobilised and beaten by members of the community. **One of
  the residents who took part in the lynching said they had beaten the suspect
  because "the police never patrols the area"**.[^treat01-exp01]

[^treat01-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a polícia
nunca patrulha o local".**

* *Treatment 02 - Criminal justice ineffectiveness*: A man was lynched last
  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
  into a house but was immobilised and beaten by members of the community.
  **One of the residents who took part in the lynching said they had beaten the
  suspect because "the judicial system is too slow and the perpetrator is on
  the street until the case is heard"**.[^treat02-exp01]

[^treat02-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a justiça
é muito lenta e os criminosos ficam soltos até o julgamento"**.

* *Treatment 03 - Demand for harsher legal punishment*: A man was lynched last
  Friday in Jundiaí, São Paulo. According to the neighbours, he tried to break
  into a house but was immobilised and beaten by members of the community.
  **One of the residents who took part in the lynching said they had beaten the
  suspect because "the judicial punishment is not harsh
  enough"**.[^treat03-exp01]

[^treat03-exp01]: In Portuguese: Um homem foi linchado na última sexta-feira em
Jundiaí, São Paulo. De acordo com vizinhos, ele tentou invadir uma residência
mas foi imobilizado e agredido por membros da comunidade. **Um dos moradores
envolvidos no linchamento disse que eles agrediram o suspeito porque "a punição
da justiça não é dura o suficiente"**.

Before each vignette, respondents read the following text:

* You will be shown a news article. Please read it carefully. After you read
  the article, we will ask you one question about it.[^vig01-exp01]

[^vig01-exp01]: In Portuguese: Uma notícia será apresentada para você. Por
favor, leia a notícia com atenção. Após você ler o artigo, faremos uma pergunta
sobre ele.

After the vignette, respondents were presented with this question:

* Do you think that the lynching was justified? Please use the slider below
  to indicate your opinion. For disagreement, use 0 to 49; for agreement,
  use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^vig02-exp01]

[^vig02-exp01]: In Portuguese: Você acha que o linchamento foi correto? Por
favor, use a barra abaixo para indicar sua opinião. Para discordar, use de 0 a
49; para concordar, use de 51 a 100. Por favor, use 50 para não concordar nem
discordar.

```{r exp01-main, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis', echo=F}
df_exp01 <- df1 %>%
  mutate(exp01_outcomes = coalesce(exp01_control, exp01_police,
                                   exp01_slow_justice, exp01_small_punishment),
         exp01_any_treat = case_when(!is.na(exp01_control) ~ "0",
                                     !is.na(exp01_police) ~ "1",
                                     !is.na(exp01_slow_justice) ~ "1",
                                     !is.na(exp01_small_punishment) ~ "1",
                                     TRUE ~ NA_character_),
         exp01_police_treat = case_when(!is.na(exp01_control) ~ "0",
                                        !is.na(exp01_police) ~ "1"),
         exp01_slow_justice_treat = case_when(!is.na(exp01_control) ~ "0",
                                              !is.na(exp01_slow_justice) ~ "1"),
         exp01_small_punishment_treat = case_when(!is.na(exp01_control) ~ "0",
                                                  !is.na(exp01_small_punishment) ~ "1"))

m1 <- lm(exp01_outcomes ~ exp01_police_treat, data = df_exp01)
m2 <- lm(exp01_outcomes ~ exp01_slow_justice_treat, data = df_exp01)
m3 <- lm(exp01_outcomes ~ exp01_small_punishment_treat, data = df_exp01)
m4 <- lm(exp01_outcomes ~ exp01_any_treat, data = df_exp01)
```

## Heterogeneous Effects

We estimate heterogeneous effects for our experiment using Bayesian Additive
Regression Trees (BART) [@chipman2010bart; @hill2011bayesian]. BART methods
allow users to detect non-linear interactions and are insensitive to the choice
of tuning parameters, so they are well-suited to analyze observational and
experimental data [@green2012modeling]. More specifically, we employ the
`bartCause` package, which is designed to estimate causal inference models. The
results are based on 800 posterior samples times 5 chains.

Results vary little in all of our estimations. We find that the personal
characteristics of the respondents have no impact on our main models, which we
report in table 1 in the article. Below we present heterogeneous effects for
the three treatment conditions we included in our experiment. We run one model
for each covariate, namely gender, age, race, education, household income, and
political ideology. To save space, here we only show the average treatment
effect within each group, but the complete results are available in section 3.4
of the extended version of the appendix ([_redacted for peer review_]).

### Treatment 01: Police Ineffectiveness

Our results indicate that the effects for this treatment arm is null in every
model specification. We find no evidence of heterogeneous effects.

\begin{table}[!htbp] \centering
\small
  \caption{Heterogeneous Effects for Treatment 1: Police Ineffectiveness}
  \label{tab:exp01het01}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
\hline \\[-1.8ex]
 Gender & 0.9729 &  &  & & & \\
  & (2.293) &  &  & & & \\
  Age &  & 1.180 &  & & & \\
  &  & (2.266) &  &  \\
  Race &  &  & 1.0668 & & &  \\
  &  &  & (2.261) & & & \\
  Education &  &  &  & 1.1463 & & \\
  &  &  &  & (2.277) & & \\
  Household Income &  &  &  & & 1.1459 & \\
  &  &  &  & & (2.290) & \\
  Political Ideology &  &  &  & & & 1.3693 \\
  &  &  &  & & & (2.225) \\
 N & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} & \multicolumn{1}{c}{1,153} \\
\hline \\[-1.8ex]
\end{tabular}
\end{table}
\normalsize

### Treatment 02: Criminal Justice Ineffectiveness

We do not find any evidence of heterogeneous treatment effects in this
condition either.

\begin{table}[!htbp] \centering
\small
  \caption{Heterogeneous Effects for Treatment 2: Criminal Justice
  Ineffectiveness}
  \label{tab:exp01het02}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
\hline \\[-1.8ex]
 Gender & -0.0752 &  &  & & & \\
  & (2.372) &  &  & & & \\
  Age &  & -0.2788 &  & & & \\
  &  & (2.379) &  &  \\
  Race &  &  & NA & & &  \\
  &  &  & (NA) & & & \\
  Education &  &  &  & 0.2204 & & \\
  &  &  &  & (2.347) & & \\
  Household Income &  &  &  & & -0.0295 & \\
  &  &  &  & & (2.331) & \\
  Political Ideology &  &  &  & & & -0.0936 \\
  &  &  &  & & & (2.339) \\
 N & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} & \multicolumn{1}{c}{1,103} \\
\hline \\[-1.8ex]
\multicolumn{5}{l}{\textbf{Note}: There are no estimates for race because some
groups have no observations.}
\end{tabular}
\end{table}
\normalsize

### Treatment 03: Demand for Harsher Legal Punishment

As in our previous estimations, we find no evidence of heterogeneous treatment effects.

\begin{table}[!htbp] \centering
\small
  \caption{Heterogeneous Effects for Treatment 3: Demand for Harsher Legal
  Punishment}
  \label{tab:exp01het03}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
\hline \\[-1.8ex]
 Gender & 0.4202 &  &  & & & \\
  & (2.331) &  &  & & & \\
  Age &  & 0.7766 &  & & & \\
  &  & (2.316) &  &  \\
  Race &  &  & 0.6672 & & &  \\
  &  &  & (2.367) & & & \\
  Education &  &  &  & 0.50238 & & \\
  &  &  &  & (2.337) & & \\
  Household Income &  &  &  & & 0.5526 & \\
  &  &  &  & & (2.307) & \\
  Political Ideology &  &  &  & & & 0.61041 \\
  &  &  &  & & & (2.298) \\
 N & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} & \multicolumn{1}{c}{1,099} \\
\hline \\[-1.8ex]
\end{tabular}
\end{table}
\normalsize

\newpage 

# Experiment 02

## Description

In our second experiment, we present five pairs of criminal profiles to
respondents. Each profile consists of eight attributes: 1) gender of the crime
perpetrator; 2) age of the crime perpetrator; 3) race of the crime perpetrator;
4) residency of crime perpetrator; 5) offense; 6) gender of the victim of the
motivating crime; 7) age of the victim of the motivating crime; 8) lynching
perpetrators. 

We added three restrictions to the conjoint design to avoid implausible
scenarios. First, female rapists were excluded from the model, but we did
include female molesters in the conjoint experiment. Second, when the offense
was car theft, the victim could not be a child. Lastly, teenagers could not be
victims of car theft either. All other combinations were allowed. We randomized
the attributes using a `php` script, which is available at
[_redacted for peer review_].

Respondents indicated which profile they preferred for extrajudicial
punishment. Prior to the experiments, they had read the following prompt:

* Lynchings are often used as social punishment in Brazil. Lynchings are cases
  in which three or more people physically attack or execute a suspected
  criminal in public. We are interested in knowing more about how Brazilians
  see these episodes. In the next five questions, please read the description
  of two possible lynching victims in Brazil and indicate in which case you
  believe the punishment is more justified. Even if you are not entirely sure,
  please select one of the cases.[^portuguese]

[^portuguese]: Original text in Portuguese: Linchamentos são às vezes usados
como punição social no Brasil. Linchamentos são casos nos quais três ou mais
pessoas agridem fisicamente ou executam em público um suspeito de um crime.
Estamos interessados em saber mais sobre como os brasileiros vêem estes
episódios. Nas próximas cinco questões, por favor, leia a descrição de duas
possíveis vítimas de linchamento no Brasil e indique em quais delas você
acredita que a punição é mais justificada. Mesmo que você não tenha certeza,
por favor, escolha um dos casos.

```{r conjoint-mm, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=5, echo=F, results = "hide"}
conjoint_data <- read.qualtrics("../data/data-conjoint.csv",
                                responses = c("Q13", "Q14", "Q15",
                                              "Q16", "Q17"),
                                covariates = c("ResponseId",
                                               "Q1", "Q2", "Q3", "Q4",
                                               "Q5", "Q6", "Q7",
                                               "Q8", "Q9", "Q10",
                                               "Q11", "Q12"),
                                new.format = FALSE, respondentID = NULL)

conjoint_data <- conjoint_data %>%
  rename(response_id                      = ResponseId,
         Age                              = Q2,
         Gender                           = Q3,
         Race                             = Q4,
         Education                        = Q5,
         Region                           = Q6,
         "Household Income"               = Q7,
         Ideology                         = Q8,
         "Support death penalty"          = Q9,
         "Previous Victimization"         = Q10,
         "Offense"                        = Crime,
         "Opinion on Policing"            = Q11,
         "Opinion on Judiciary"           = Q12,
         "Gender of crime victim"         = "Gênero.da.vítima",
         "Gender of crime perpetrator"    = "Gênero.do(a).criminoso(a)",
         "Age of crime victim"            = "Idade.da.vítima",
         "Age of crime perpetrator"       = "Idade.do(a).criminoso(a)",
         "Lynching perpetrators"          = "Linchadores",
         "Race of crime perpetrator"      = "Raça.do(a).criminoso(a)",
         "Residency of crime perpetrator" = "Residência.do.criminoso") %>%
  mutate(`Gender of crime perpetrator` = fct_recode(`Gender of crime perpetrator`,
                                                    "Male"   = "Masculino",
                                                    "Female" = "Feminino"),
         `Age of crime perpetrator` = fct_recode(`Age of crime perpetrator`,
                                                 "Teenager" = "Adolescente",
                                                 "Adult"    = "Adulto(a)",
                                                 "Elderly"  = "Idoso(a)"),
         `Race of crime perpetrator` = fct_recode(`Race of crime perpetrator`,
                                                  "Asian"      = "Asiático(a)",
                                                  "White"      = "Branco(a)",
                                                  "Indigenous" = "Indígena",
                                                  "Black"      = "Negro(a)"),
         `Residency of crime perpetrator` = fct_recode(`Residency of crime perpetrator`,
                                                       "Another neighborhood" = "Mora em outro bairro",
                                                       "In the neighborhood"  = "Mora na vizinhança"),
         `Offense` = fct_recode(`Offense`,
                                "Murder"         = "Assassinou",
                                "Pick-pocketing" = "Bateu a carteira",
                                "Rape"           = "Estuprou",
                                "Molestation"    = "Molestou",
                                "Car theft"      = "Roubou o carro"),
         `Gender of crime victim` = fct_recode(`Gender of crime victim`,
                                               " Male"   = "Masculino",
                                               " Female" = "Feminino"),
         `Age of crime victim` = fct_recode(`Age of crime victim`,
                                            " Teenager" = "Adolescente",
                                            " Child"    = "Criança",
                                            " Adult"    = "Adulto(a)",
                                            " Elderly"  = "Idoso(a)"),
         `Lynching perpetrators` = fct_recode(`Lynching perpetrators`,
                                              "Family of the victim" = "Família da vítima",
                                              "Gangs"                = "Gangues",
                                              "Bystanders"           = "Pedestres",
                                              "Police"               = "Polícia",
                                              "Neighbors"            = "Vizinhos")) %>%
  select(-c(16, 18, 20, 22, 24, 26, 28, 30)) %>%
  mutate(response_id = tolower(response_id))

# Model
fm <- selected ~ `Gender of crime perpetrator` +
  `Age of crime perpetrator` + `Race of crime perpetrator` +
  `Residency of crime perpetrator` + `Offense` +
  `Gender of crime victim` + `Age of crime victim` +
  `Lynching perpetrators`

mms <- mm(conjoint_data, fm, id = ~response_id, h0 = 0.5)

# Plot
faces <- c(rep("plain", 5), "bold",
           rep("plain", 4), "bold",
           rep("plain", 2), "bold",
           rep("plain", 5), "bold",
           rep("plain", 2), "bold",
           rep("plain", 4), "bold",
           rep("plain", 3), "bold",
           rep("plain", 2), "bold")

# Table
table_mm <- function(mms, capt) {
dfr <- data.frame(feature = mms[, c(4)],
                  round(mms[, c(5, 6, 8, 9, 10)], digits = 3))
names(dfr) <- c("Feature", "Estimate", "Std. Error",
                "P-Value", "Lower", "Upper")
return(kbl(dfr, "latex", caption = capt, linesep = "",
           booktabs = TRUE) %>%
kable_styling(font_size = 12, full_width = TRUE,
              latex_options = "hold_position") %>%
pack_rows("Gender of crime perpetrator", 1, 2) %>%
pack_rows("Age of crime perpetrator", 3, 5) %>%
pack_rows("Race of crime perpetrator", 6, 9) %>%
pack_rows("Residency of crime perpetrator", 10, 11) %>%
pack_rows("Offense", 12, 16) %>%
pack_rows("Gender of crime victim", 17, 18) %>%
pack_rows("Age of crime victim", 19, 22) %>%
pack_rows("Lynching perpetrators", 23, 27) %>%
column_spec(1, width = "6cm"))
}
```

## Average Marginal Component Effect (AMCE) Estimator

In the article, we estimate the conjoint experiment with the `cregg` package
[@leeper2018cregg] for the `R` statistical language [@rstats2019]. Here we also
present AMCE coefficients for the same experiment. This method selects one
reference category for each attribute and looks at changes from the baseline
level. The reference categories are marked as zero in our models.

\vspace{.3cm}

```{r conjoint-amce, warning=F, error=F, message=F, cache=T, fig.width=8, fig.height=5, echo=F, echo=F}
amces <- cj(conjoint_data, fm, id = ~response_id)

plot(amces, vline = 0.0, header_fmt = "%s") +
  theme(legend.position = "none",
        axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)
```

## Subgroup Analyses

In this subsection, we test whether our results vary according to individual
characteristics, such as gender, age, race, income, support for death penalty,
and the respondents' opinions on the judicial system and the police forces. All
models report marginal means. As we shall see, the results are very robust
across all model specifications.

### Gender

Results do not seem to vary according to the gender of the respondent. We focus
here on the differences between males and females and exclude the 11
observations in which respondents preferred not to say their gender or marked
"other" in our questionnaire. Across all conjoint experiment attributes, we see
an overlap between the 95% confidence intervals for males and females.

\vspace{.3cm}
```{r conjoint-females, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5, fig.pos = "H", echo=F}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(gender) %>%
  filter(gender == c("Male", "Female"))
cjdt$Gender <- factor(cjdt$gender)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Gender)

# Plot
plot(mm_by, group = "Gender", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)
```

### Age

As our age variable is continuous, we divide the data into three age brackets:
18-34 years old, 35-54 years old, and 55+ years old. The results show that
seniors (55+) are more likely to select profiles that include murder as an
offense, and less inclined to choose cases involving molestation. The remaining
attributes show little variation.

\vspace{.3cm}
```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=4.6, fig.pos="H", echo=F}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(age) %>%
  mutate(age2 = case_when(age >= 18 & age <= 34 ~ "18-34", age >= 35 & age <= 54 ~ "35-54",
                          age >= 55 ~ "55 plus", TRUE ~ as.character(age)))
cjdt$Age <- factor(cjdt$age2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Age)

# Plot
plot(mm_by, group = "Age", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
```

### Race

Below are our results when we disaggregate the data by race. We find that they are
almost identical is all dimensions except for offense. Asian respondents are
much less likely to select profiles that contain pickpocketing as a crime.

\vspace{.3cm}
```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5, fig.pos="H", echo=F}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(race) %>%
  filter(race == c("Asian", "Black", "Mixed Race", "White"))
cjdt$Race <- factor(cjdt$race)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Race)

# Plot
plot(mm_by, group = "Race", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)
```

### Education

Next, we divide our data according to respondents' level of education. As the
number of interviewees with primary or secondary education is low, we merge
them into a single category, while the other levels (high school, college, and
graduate school) remain the same as in our questionnaire.

\vspace{.5cm}
```{r conjoint-education, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5, fig.pos="H", echo=F}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(education) %>%
  filter(education == c("College", "Graduate School",
                        "Primary School", "Secondary School",
                        "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ as.character(education)),
         education2 = fct_relevel(education2, "Primary or Secondary School",
                                  "High School", "College", "Graduate School"))
cjdt$Education <- factor(cjdt$education2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Education)

# Plot
plot(mm_by, group = "Education", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)

```

### Household Income

We also disaggregate the results by monthly household income. As some
categories have few respondents, we group them into three categories: (i) up to
R\$3,000 (US\$550); (ii) from R\$3,001 to R\$5,000 (US\$550-915); and (iii)
above R\$5,000 (US\$915+). The levels roughly represent low, middle, and
high-income households. We find no considerable differences among them.

\vspace{.3cm}
```{r conjoint-income, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=4.5, fig.pos="H", echo=F}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(household_income) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_),
         household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
                                         "Above R$5,000"))
cjdt$Income <- factor(cjdt$household_income2)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by = ~Income)

# Plot
plot(mm_by, group = "Income", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)
```

### Political Ideology

Here we disaggregate the results according to political ideology. We see that
political views do not change the overall responses.

\vspace{.5cm}
```{r conjoint-ideology, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.2, fig.pos="H", echo=F}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(ideology)
cjdt$Ideology <- factor(cjdt$ideology)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm", h0 = 0.5, by =
            ~Ideology)

# Plot
plot(mm_by, group = "Ideology", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)
```

## Text Analysis

In addition to the conjoint experiments, we also asked respondents to justify
their profile choices. We added a text box after each conjoint and informed
subjects that their responses were optional. However, we obtained `r (nrow(df1) - sum(is.na(df1$q13_text))) + (nrow(df1) - sum(is.na(df1$q14_text))) + (nrow(df1) - sum(is.na(df1$q15_text))) + (nrow(df1) - sum(is.na(df1$q16_text))) + (nrow(df1) - sum(is.na(df1$q17_text)))` responses
in our survey, which we analyze here.

First, we concatenate all text responses into a single vector. Then we tokenize
the sentences, remove Portuguese stop words and punctuation, and select the
words that appear most frequently in the texts.

The graphs shows that _crime_ (same as in English), _porque_ (because),
_linchamento_ (lynching), and _caso_ (case) are the words respondents use most
often. This is expected as subjects were asked to justify their choices. The
next words in the list are related to victim or crime characteristics, such as
_criança_ (child), _estupro_ (rape), _assassinato_ (murder), and _vítima_
(victim). Indeed, they provide evidence for our previous findings and confirm
that respondents select lynching victim profiles according to these two
factors. Criminal characteristics, such as age or race, do not seem to be
particularly relevant, as respondents do not mention them as much. The
following terms are _nenhum_ (none), _contra_ (against), _acho_ (I think),
_casos_ (cases), _ter_ (have to), and _justiça_ (justice). We believe these
words correspond to cases where respondents wanted to affirm that they do not
have any preference regarding the lynching profiles, or that they would rather
not have chosen any of the alternatives.

\vspace{.3cm}
```{r conjoint-text, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=4.5, fig.pos="H", fig.cap = "Words respondents use most frequently when justifying their choices of lynching profiles", echo=F}
dfmat <- df1 %>%
  select(q13_text, q14_text, q15_text, q16_text, q17_text) %>%
  gather() %>%
  corpus(text_field = "value") %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE,
         remove_symbol = TRUE) %>%
  dfm() %>%
  dfm_remove(., pattern = c(stopwords("pt", source = "snowball"),
                            "é", "ser"))
dfmat %>%
  textstat_frequency(n = 15) %>%
  ggplot(aes(x = reorder(feature, frequency), y = frequency)) +
  geom_point(colour = "#152238") +
  coord_flip() +
  labs(x = NULL, y = "Frequency") +
  theme_minimal()
```

We also construct a feature co-occurrence matrix (FCM) that shows which words
appear together in the responses we collected. Again, the results confirm the
findings of the conjoint experiment. As suggested in the previous graph, we see
a central cluster that describes crime and victim characteristics and includes
the words _linchamentos_ (lynchings), _caso_ (case), _estupro_ (rape),
_criança_ (child), _assassinato_ (murder), and _vítima_ (victim). This
highlights that these are the most important reasons why respondents choose
lynching profiles.

We note that there is another word cluster on the left. It contains words
that indicate that some respondents do not support lynchings, such as _não_
(no), _opção_ (choice), _nada_ (nothing), _justifica_ (justifies),
_justificável_ (justifiable), and _escolher_ (choose).

\vspace{.3cm}
```{r conjoint-fcm, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=3, fig.pos="H", fig.cap = "Semantic network analysis", echo=F}
fcmat <- fcm(dfmat)
feat <- names(topfeatures(fcmat, 70))
fcmat_select <- fcm_select(fcmat, pattern = feat, selection = "keep")
size <- log(colSums(dfm_select(dfmat, feat, selection = "keep")))

# Plot
set.seed(144)
textplot_network(fcmat_select, min_freq = 0.8, vertex_size = size / max(size) * 3, max.overlaps = 30)
```

We estimate a latent Dirichlet allocation (LDA) model to identify the three
most important topics in our corpus. The first topic includes words that refer
to victim and crime characteristics, many of which have also appeared in our
previous estimations. Some of the most common words in this group are _crime_
(crime), _criança_ (child), _estupro_ (rape), _vítima_ (victim), _porque_
(because), _idoso_ (elderly), _grave_ (serious), and _molestar_ (molest). When
we count the number of topics in the corpus, we see that this is the
predominant one. The second topic identified by the model describes lynching
perpetrators, as it contains the words like _polícia_ (police), _pessoas_
(people), and _família_ (family). The third topic identifies the same words we
associate with respondents who are against lynchings, such as _nenhum_ (none),
_opção_ (choice), _não_ (no), and _contra_ (against). As our results show,
respondents decide which individual deserves punishment based on factors
related to the crime he/she committed, especially the crime victim. There is
also a group of respondents that oppose lynchings in principle, who affirm that
lynchings are never justified.

\footnotesize
```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=10, fig.height=9, fig.post="H", echo=F}
# Unsupervised LDA
tmod_lda <- textmodel_lda(dfmat, k = 3)
terms(tmod_lda, 10)
table(topics(tmod_lda))
```
\normalsize

Our last model is a semisupervized LDA, in which we include a series of
keywords to measure how frequently some pre-defined topics appear often in the
responses. We adopt a conservative approach and only include words that we have
a high degree of confidence that are not ambiguous. There are four pre-defined
topics in this estimation. The first refers to victims, and include the
Portuguese words for _children_, _life_, and _victim_ (along with possible
variations). The second topic describes crime characteristics with words such
as _murder_, _rape_, _kill_, _molest_, and _steal_. The next group has four
keywords that describe lynching perpetrators, and they are _gangs_, _family_,
_bystanders_, and _police_. The fourth topic includes terms to identify
respondents who are against lynchings, and we added _against_, _none_, _do not
agree_, and _choice_ as seed terms. We see that the topic describing crime
characteristics is the one that appears more often.

\footnotesize
```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H", echo=F}
# Semisupervised LDA
keywords <- dictionary(list(victim      = c("crian*", "vida*", "v*tima*"),
                            crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
                            perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
                            against     = c("contra", "escolha", "nenhum*", "n*o concord*", "op**o")))

slda <- textmodel_seededlda(dfmat, keywords, residual = TRUE)
terms(slda, 10)
table(topics(slda))
```
\normalsize

# Experiment 03

## Description

Our last experiment measures the effect of information provision on attitudes
about lynching. In particular, we test whether reminding respondents
about the legal and social consequences of vigilante justice reduces the
subjects' level of support for such practice.

The experiment has three treatment conditions and a control group. In all of
them we present respondents with a short statement affirming that some
Brazilians support vigilantism under certain conditions. Respondents were asked
to use 0 to 49 if they disagree, 50 if they neither agree nor disagree, and
50-100 if they agree with the sentence.

Each of the three treatment groups received a different message about the
legal or social consequences of lynching in Brazil. In the first treatment
arm, we informed subjects about how the Brazilian constitution and penal code
punishes civilian violence. The second treatment group was notified about
the human rights guarantees enshrined in Brazil's legal framework. The last
group read a vignette that mentions how lynchings can spark _vendettas_ and
initiate a cycle of violence in the community. Subjects in the control group
received no information about the consequences of lynchings. The text shown
to the control and treatment groups can be read below.

* *Control group*: In Brazil, some people believe that lynching may be
  justified under certain conditions. To what degree do you agree or disagree
  that lynching can be justified? Please use the slider below to indicate your
  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
  Please use 50 if you neither agree nor disagree.[^control-exp03]

[^control-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. O quanto você concorda ou
discorda que linchamentos podem ser justificados? Por favor, use a barra abaixo
para indicar sua preferência. Para indicar que discorda, use de 0 a 49; para
concordar, use de 51 a 100. Por favor, use 50 caso você não concorde nem
discorde.

* *Treatment 01 - Legal punishment for lynching perpetrators*: In Brazil,
  some people believe that lynching may be justified under certain conditions.
  **However, the Brazilian constitution and penal code strictly forbid
  lynching and those involved can be accused of torture or murder**. To what
  degree do you agree or disagree that lynching can be justified? Please use
  the slider below to indicate your preference. For disagreement, use 0 to 49;
  for agreement, use 51 to 100. Please use 50 if you neither agree nor
  disagree.[^treat01-exp03]

[^treat01-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, a
constituição e o código penal do Brasil proíbem estritamente os linchamentos e
os envolvidos podem ser acusados de tortura ou assassinato.** O quanto você
concorda ou discorda que linchamentos podem ser justificados? Por favor, use a
barra abaixo para indicar sua preferência. Para indicar que discorda, use de 0
a 49; para concordar, use de 51 a 100. Por favor, use 50 caso você não concorde
nem discorde.

* *Treatment 02 - Human rights*: In Brazil, some people believe that lynching
  may be justified under certain conditions. **However, the Brazilian
  constitution states that all individuals have the right of not being
  tortured, including criminals**. To what degree do you agree or disagree that
  lynching can be justified? Please use the slider below to indicate your
  preference. For disagreement, use 0 to 49; for agreement, use 51 to 100.
  Please use 50 if you neither agree nor disagree.[^treat02-exp03]

[^treat02-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, a
constituição do Brasil afirma que todos os indivíduos têm o direito de não
serem torturados, inclusive criminosos**. O quanto você concorda ou discorda que
linchamentos podem ser justificados? Por favor, use a barra abaixo para indicar
sua preferência. Para indicar que discorda, use de 0 a 49; para concordar, use
de 51 a 100. Por favor, use 50 caso você não concorde nem discorde.

* *Treatment 03 - Vendettas*: In Brazil, some people believe that lynching
  may be justified under certain conditions. **However, lynchings can trigger
  a new cycle of violence as the family or friends of the victim may retaliate
  the community**. To what degree do you agree or disagree that lynching can be
  justified? Please use the slider below to indicate your preference. For
  disagreement, use 0 to 49; for agreement, use 51 to 100. Please use 50 if you
  neither agree nor disagree.[^treat03-exp03]

[^treat03-exp03]: In Portuguese: No Brasil, algumas pessoas acreditam que
linchamentos são justificados sob certas condições. **Entretanto, linchamentos
podem iniciar um ciclo de violência pois a família ou amigos da vítima podem
retaliar a comunidade**. O quanto você concorda ou discorda que linchamentos
podem ser justificados? Por favor, use a barra abaixo para indicar sua
preferência. Para indicar que discorda, use de 0 a 49; para concordar, use de
51 a 100. Por favor, use 50 caso você não concorde nem discorde.

```{r exp03-main, warning=F, message=F, error=F, cache=T, echo=F}
df_exp03 <- df1 %>%
  mutate(exp03_outcomes = coalesce(exp03_control, exp03_constitution, exp03_rights, exp03_vendetta),
         exp03_any_treat = case_when(!is.na(exp03_control) ~ "0", !is.na(exp03_constitution) ~ "1",
                                     !is.na(exp03_rights) ~ "1", !is.na(exp03_vendetta) ~ "1",
                                     TRUE ~ NA_character_),
         exp03_constitution_treat = case_when(!is.na(exp03_control) ~ "0",
                                              !is.na(exp03_constitution) ~ "1"),
         exp03_rights_treat = case_when(!is.na(exp03_control) ~ "0",
                                        !is.na(exp03_rights) ~ "1"),
         exp03_vendetta_treat = case_when(!is.na(exp03_control) ~ "0",
                                          !is.na(exp03_vendetta) ~ "1"))

m1 <- lm(exp03_outcomes ~ exp03_constitution_treat, data = df_exp03)
m2 <- lm(exp03_outcomes ~ exp03_rights_treat, data = df_exp03)
m3 <- lm(exp03_outcomes ~ exp03_vendetta_treat, data = df_exp03)
m4 <- lm(exp03_outcomes ~ exp03_any_treat, data = df_exp03)
```
\normalsize

## Determinants of Baseline Levels

As we did in the first experiment, we evaluate how individual characteristics
impact lynching support. The results are similar to those presented in table
\ref{tab:exp03baseline}, with the exception that the coefficient for white
respondents is negative in two estimations, and the coefficient for male does
not reach statistical significance in the last model ($p$-value = 0.11).

```{r exp03-baseline, warning=F, message=F, error=F, cache=T, fig.pos="ht", results='asis', echo=F}
df_exp03_group <- df_exp03 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White"),
         ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
  mutate(race = fct_relevel(race, "Black"), ideology = fct_relevel(ideology, "Center"))

df_exp03_gender <- df_exp03 %>% filter(gender == c("Female", "Male"))
df_exp03_race <- df_exp03 %>% filter(race %in% c("Asian", "Black", "Mixed Race", "White")) %>%
  mutate(race = fct_relevel(race, "Black"))
df_exp03_ideology <- df_exp03 %>%
         filter(ideology %in% c("Center", "Center-Left", "Center-Right", "Left", "Right")) %>%
         mutate(ideology = fct_relevel(ideology, "Center"))

m1 <- lm(exp03_outcomes ~ gender, data = df_exp03_gender)
m2 <- lm(exp03_outcomes ~ race, data = df_exp03_race)
m3 <- lm(exp03_outcomes ~ ideology, data = df_exp03_ideology)
m4 <- lm(exp03_outcomes ~ gender + race + ideology, data = df_exp03_group)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4), p = starprep(m1, m2, m3, m4, stat = "p.value"),
          header = FALSE, align = TRUE, label = "tab:exp03baseline",
          title = "Experiment 01 -- Determinants of Baseline Levels of
          Lynching Support", style = "apsr", dep.var.labels = "\\textbf{Lynching Support}\\vspace{.5cm}",
          covariate.labels = c("Male", "Asian", "Mixed Race", "White",
                               "Left", "Center-Left", "Center-Right", "Right"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE, 
          table.placement = "ht")
```

## Heterogeneous Effects

In this section, we explore whether our pre-treatment covariates impact the
treatment effect. We use the same flexible approach we employed in the previous
experiment, and estimate all models using Bayesian Additive Regression Trees
(BART). The algorithm produces average treatment effects for each category in
the moderator variables.

### Treatment 01: Legal Punishment for Lynching Perpetrators

We find no evidence of heterogeneous effects in this treatment condition. All
coefficients are largely similar across all model specifications.

\begin{table}[!htbp] \centering
\small
  \caption{Heterogeneous Effects for Treatment 1: Legal Punishment for Lynching Perpetrators}
  \label{tab:exp03het01}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
\hline \\[-1.8ex]
 Gender & -4.454 &  &  & & & \\
  & (2.234) &  &  & & & \\
  Age &  & -4.459 &  & & & \\
  &  & (2.208) &  &  \\
  Race &  &  & -4.3069 & & &  \\
  &  &  & (2.220) & & & \\
  Education &  &  &  & -4.486 & & \\
  &  &  &  & (2.190) & & \\
  Household Income &  &  &  & & -4.520 & \\
  &  &  &  & & (2.206) & \\
  Political Ideology &  &  &  & & & -4.5719 \\
  &  &  &  & & & (2.175) \\
 N & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} & \multicolumn{1}{c}{1,109} \\
\hline \\[-1.8ex]
\end{tabular}
\end{table}
\normalsize

### Treatment 02: Human Rights

Our results show no presence of heterogeneous effects.

\begin{table}[!htbp] \centering
\small
  \caption{Heterogeneous Effects for Treatment 2: Human Rights}
  \label{tab:exp03het02}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
\hline \\[-1.8ex]
 Gender & -1.598 &  &  & & & \\
  & (2.228) &  &  & & & \\
  Age &  & -1.5594 &  & & & \\
  &  & (2.196) &  &  \\
  Race &  &  & -1.533 & & &  \\
  &  &  & (2.209) & & & \\
  Education &  &  &  & -1.5033 & & \\
  &  &  &  & (2.188) & & \\
  Household Income &  &  &  & & -1.3378 & \\
  &  &  &  & & (2.184) & \\
  Political Ideology &  &  &  & & & -1.4722 \\
  &  &  &  & & & (2.155) \\
 N & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} & \multicolumn{1}{c}{1,168} \\
\hline \\[-1.8ex]
\end{tabular}
\end{table}
\normalsize

### Treatment 03: Vendettas

We do not find considerable heterogeneity in these last results. Overall, the
three treatment conditions are very stable, thus we are confident that the main
results are not driven by any particular group.

\begin{table}[!htbp] \centering
\small
  \caption{Heterogeneous Effects for Treatment 3: Vendettas}
  \label{tab:exp03het03}
\begin{tabular}{@{\extracolsep{3pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} }
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{\textbf{Lynching Support}\vspace{.5cm}} \\
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)} & \multicolumn{1}{c}{(5)} & \multicolumn{1}{c}{(6)}\\
\hline \\[-1.8ex]
 Gender & -3.114 &  &  & & & \\
  & (2.356) &  &  & & & \\
  Age &  & -2.574 &  & & & \\
  &  & (2.303) &  &  \\
  Race &  &  & -3.0267 & & &  \\
  &  &  & (2.291) & & & \\
  Education &  &  &  & -3.076 & & \\
  &  &  &  & (2.271) & & \\
  Household Income &  &  &  & & -2.738 & \\
  &  &  &  & & (2.295) & \\
  Political Ideology &  &  &  & & & -2.8907 \\
  &  &  &  & & & (2.265) \\
 N & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} & \multicolumn{1}{c}{1,086} \\
\hline \\[-1.8ex]
\end{tabular}
\end{table}
\normalsize

\newpage 

# Ethics Statement

We adhered to the ethical guidelines provided by the Institutional Review Board
at Brown University and APSA's Principles and Guidance. To facilitate
transparency, we comment here on a few aspects of our research design. First,
we worked with the Brown University IRB to reduce the risk of harm for
participants taking the survey. This included consultation with a cultural
expert to inform the phrasing of the survey. Second, respondents received
compensation via Qualtrics, which paid respondents directly after they completed
the questionnaire. Each subject in Qualtrics' online panel received the
equivalent of 2.5 USD in Brazilian Reals (local currency). Respondents who do
not finish the survey will not receive compensation. The compensation is
appropriate for the participant population. As of August 17, 2020, Brazil's
monthly minimum wage is BRL1039, which amounts to 191 US dollars. Assuming 40
working hours per week, the hourly minimum wage equals 1.19 US dollars. Our
survey takes about 20 minutes to complete and respondents received 2.5 USD,
therefore subjects will receive a monetary compensation that is 6 times higher
than the local minimum wage. Third, we do not see any potential or perceived
conflicts of interest in carrying out this research. We received a grant of
$10,000 to conduct this research from the Centre for the Study of Governance &
Society at King’s College London, which receives support from the Templeton
Foundation. We are aware of no conflicts of interest from either source. All of
the code and data will be made publicly available. 

\newpage
